The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-12 paper/main.tex
add RV bias note

The hypothesis that binarity might matter is grounded in the fact that radial 
velocity and transit surveys treat binarity differently.
Radial velocity surveys typically reject both visual and spectroscopic binaries
\citep[\textit{e.g.},][]{wright_frequency_2012}.
Transit surveys observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a tendency against confirming 
transiting planets in binary systems.

@@

We then gave a general formula for the apparent rate density inferred by an 
observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
As input, this equation requires a volume-limited mass ratio distribution 
$f(q)$, and the true rate densities for planets around singles, 
primaries, and secondaries.
The assumptions that make the model tractable are:
\begin{enumerate}
    \item the transit survey is SNR-limited;
    \item the true properties of all the singles and primaries are known to 
    the observer;
    \item the observers assume that binaries have the same properties as the 
    primaries;
    \item there are functions $L(M)$ and $R(M)$ that specify a star's 
    luminosity and radius in terms of its mass.
\end{enumerate}
Allowing for these conditions, many results follow:
\begin{itemize}
%
\item Assuming a power-law planet radius distribution, and that the same 
number of planets orbit singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
17r_\oplus$ (Sec.~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with 
\citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a constant 
occurrence at $r < 2r_\oplus$, there is a ``bump'' in the apparent rate 
density at $r\a < 2r_\oplus$, leading to a relative error $\delta \Gamma_0 = 
|\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
(Fig.~\ref{fig:occ_rate_model_3_log}).
Although this is smaller than current systematic uncertainties on the 
occurrence rates of Earth-sized planets, this means that binarity could
eventually become an important component of the $\eta_\oplus$ error budget.
%
\item Binarity ``fills in'' gaps in the radius distribution 
(Fig.~\ref{fig:model_4}), by an amount that could affect precise measurements 
of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
gap, in the event that planets are not carefully vetted with high resolution 
imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates 
(Fig.~\ref{fig:gaussian_HJ}).
This assumes a Gaussian planet radius distribution, similar to that reported 
by~\citet{petigura_CKS_2017}.
%
\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are revealed by 
high resolution imaging surveys to exist in binaries are more likely to orbit 
the primary (Fig.~\ref{fig:frac_model_3}).
%
\item Near the ``break'' in the true rate distribution ($\approx 2r_\oplus$), 
the fraction of detected planets with binary companions increases
(Fig.~\ref{fig:frac_model_3}).
\end{itemize}

@@

\acknowledgements{
It was a pleasure sharing discussions about this study with F. Dai and T. 
Barclay.
This work made use of NASA's Astrophysics Data System Bibliographic Services.

>>>>

The hypothesis that binarity might matter is grounded in the fact that radial 
velocity and transit surveys treat binarity differently.
Radial velocity surveys typically reject both visual and spectroscopic binaries
\citep[\textit{e.g.},][]{wright_frequency_2012}.
Transit surveys observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of transiting planet candidates, the prevalence of 
astrophysical false-positives may also lead to a tendency against confirming 
transiting planets in binary systems.
A separate observational bias is that the RV surveys typically observe 
chromospherically ``quiet'' stars, which may bias their detection probability 
high~\citep{bastien_radial_2014}.

@@

We then gave a general formula for the apparent rate density inferred by an 
observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
As input, this equation requires a volume-limited mass ratio distribution 
$f(q)$, and the true rate densities for planets around singles, 
primaries, and secondaries.
The assumptions that make the model tractable are:
\begin{enumerate}
    \item the transit survey is SNR-limited;
    \item the true properties of all the singles and primaries are known to 
    the observer;
    \item the observers assume that binaries have the same properties as the 
    primaries;
    \item there are functions $L(M)$ and $R(M)$ that specify a star's 
    luminosity and radius in terms of its mass.
\end{enumerate}
Allowing for these conditions, many results follow:
\begin{itemize}
%
\item Assuming a power-law planet radius distribution, and that the same 
number of planets orbit singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
17r_\oplus$ (Sec.~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with 
\citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a constant 
occurrence at $r < 2r_\oplus$, there is a ``bump'' in the apparent rate 
density at $r\a < 2r_\oplus$, leading to a relative error $\delta \Gamma_0 = 
|\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
(Fig.~\ref{fig:occ_rate_model_3_log}).
Although this is smaller than current systematic uncertainties on the 
occurrence rates of Earth-sized planets, this means that binarity could
eventually become an important component of the $\eta_\oplus$ error budget.
%
\item Binarity ``fills in'' gaps in the radius distribution 
(Fig.~\ref{fig:model_4}), by an amount that could affect precise measurements 
of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
gap, in the event that planets are not carefully vetted with high resolution 
imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates 
(Fig.~\ref{fig:gaussian_HJ}).
This assumes a Gaussian planet radius distribution, similar to that reported 
by~\citet{petigura_CKS_2017}.
%
\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are revealed by 
high resolution imaging surveys to exist in binaries are more likely to orbit 
the primary (Fig.~\ref{fig:frac_model_3}).
%
\item Near the ``break'' in the rate distribution ($\approx 2r_\oplus$), 
the fraction of detected planets with binary companions increases by 
$\approx 5-10\%$ (Fig.~\ref{fig:frac_model_3}).
\end{itemize}

@@

\acknowledgements{
It was a pleasure sharing discussions about this study with T. Barclay, W. 
Bhatti, and F. Dai.
This work made use of NASA's Astrophysics Data System Bibliographic Services.
